### 2014-12-07 Draft/abstract.tex
Laurie's Comments

Temporal constraints of an Application Programming Interface (API)
are the allowed sequences of method invocations in the API.
These constraints govern the secure and robust operation of client software using the API.
However, in practice, most API do not have formal temporal constraints.
In contrast, these constraints are typically described
informally in natural language API documents and therefore are not amenable
to existing program analysis tools that require formal constraints.
\textit{The goal of this work is to assist developers construct API clients that comply with 
temporal constraints of the API through the inference and formalization of these constraints found in natural language text in API documents.}
Since, API documents are often verbose manually writing formal temporal constraints can be prohibitively time consuming and error prone.
To address this issue,
we propose \tool, a Machine Learning (ML) and Natural Language Processing (NLP) based
approach to identify and infer formal temporal constraints.
To evaluate our approach, we apply \tool\ to infer and formalize temporal
constraints from \amazonAPI, \paypalAPI\ and commonly used package \CodeIn{java.io} in the
JDK API.
Our results indicate that \tool\ is effective in identifying constraint sentences (from over
4000 human-annotated API sentences) with the average precision, recall, and F-score
of 77.0\%, 60.0\%, and 65.0\%, respectively.
Furthermore, \tool\ also achieves an accuracy of 70\% in inferring 63 formal temporal constraints from these sentences.

>>>>

Temporal constraints of an Application Programming Interface (API)
are the allowed sequences of method invocations in the API.
These constraints govern the secure and robust operation of client software using the API.
However, in practice, most API do not have formal temporal constraints.
In contrast, these constraints are typically described
informally in natural language API documents, and therefore are not amenable
to existing program analysis tools that require formal constraints.
\textit{The goal of this work is to assist developers construct API clients that comply with 
temporal constraints of the API through the inference and formalization of these constraints found in natural language text in API documents.}
Since, API documents are often verbose, manually writing formal temporal constraints can be prohibitively time consuming and error prone.
To address this issue,
we propose \tool, a Machine Learning (ML) and Natural Language Processing (NLP) based
approach for identifying and inferring formal temporal constraints.
To evaluate our approach, we apply \tool\ to infer and formalize temporal
constraints from \amazonAPI, \paypalAPI\ and \CodeIn{java.io} package in the
JDK API.
Our results indicate that \tool\ is effective in identifying constraint sentences (from over
4000 human-annotated API sentences) with the average precision, recall, and F-score
of 77.0\%, 60.0\%, and 65.0\%, respectively.
Furthermore, \tool\ also achieves an accuracy of 70\% in inferring 63 formal temporal constraints from these sentences.

### 2014-12-07 Draft/introduction.tex
Laurie's Comments

Application Programming Interfaces (APIs) have evolved from traditional libraries that are in the format of locally stored binary files and are programming language specific,
to web APIs that are designed to leverage the web server and web browser architecture and the implementation is programming language agnostic.
However, APIs (whether traditional or web-based) have some rules or constraints governing the proper use of the API that must be followed.
One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
Non-compliance to such constraints will often result in faulty applications that are unreliable to use and may even result in financial losses.

@@

Formal analysis tools such as model checker and runtime verifiers can assist in detection of the violations of the temporal constraints in API clients as defects~\cite{lee2012towards}.
However, such tools typically accept formal representation of the temporal constraints for detecting violations.
In contrast, temporal constraints are typically described in natural language text of API documents.
Such documents are provided to client-code developers through an online access, or are shipped with the API wrapper code.
For a method under consideration, an API document may describe both the constraints on the method parameters
as well as the temporal constraints in terms of other methods that must be invoked pre/post invoking that method.
%We observe that a non-trivial portion (roughly 12\%) of the sentences (constraint-describing sentences)
%in \amazonAPI\ documentation describe temporal constraints.

@@

To reduce the manual effort, we propose \tool: a Machine Learning (ML) and Natural Language Processing (NLP) based approach
to automatically infer formal temporal constraints. 
We propose to first employ ML for identifying temporal constraint sentences and then use NLP techniques to infer formal constraints from the identified sentences. 
Besides the generic challenges of applying NLP techniques on software related artifacts~\cite{pandita12:inferring},
our approach addresses two major challenges to automatically infer specifications from natural language text in API documents

First, classifying temporal constraint sentences is difficult. A keyword-based filtering or rule-based approach for identifying constraint sentences is often unsatisfactory, because the method names (and synonyms) are part of the keywords themselves, thus resulting an large number of keywords.
Furthermore, keywords often have confounding effects that inversely affects accuracy.
To, address this challenge, we propose to train a classification model based on generic semantic and syntactic features instead of the keywords-based features.

>>>>

Application Programming Interfaces (APIs) have evolved from traditional libraries that are in the format of locally stored binary files and are programming language specific,
to web APIs that are designed to leverage the web server and web browser architecture and the implementation is programming language agnostic.
However, APIs (whether traditional or web-based) have some constraints governing the proper use of the API that must be followed.
One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
Non-compliance to such constraints will often result in faulty applications that are unreliable to use and may even result in financial losses.

@@

Formal analysis tools, such as model checker and runtime verifiers can assist in detection of the violations of the temporal constraints in API clients as defects~\cite{lee2012towards}.
These tools typically accept formal representation of the temporal constraints for detecting violations.
However, temporal constraints are typically described in natural language text of API documents.
Such documents are provided to client-code developers through an online access, or are shipped with the API wrapper code.
For a method under consideration, an API document may describe both the constraints on the method parameters
as well as the temporal constraints in terms of other methods that must be invoked pre/post invoking that method.
%We observe that a non-trivial portion (roughly 12\%) of the sentences (constraint-describing sentences)
%in \amazonAPI\ documentation describe temporal constraints.

@@

To reduce the manual effort, we propose \tool: a Machine Learning (ML) and Natural Language Processing (NLP) based approach
to automatically identify and infer formal temporal constraints. 
We propose to first employ ML for identifying temporal constraint sentences and then use NLP techniques to infer formal temporal constraints from the identified sentences.

Besides the generic challenges of applying NLP techniques on software related artifacts~\cite{pandita12:inferring},
our approach addresses two major challenges to automatically infer specifications from natural language text in API documents

First, identifying temporal constraint sentences is difficult. A keyword-based filtering or rule-based approach for identifying constraint sentences is often unsatisfactory, because the method names (and synonyms) are part of the keywords themselves, thus resulting in a large number of keywords.
Furthermore, keywords often have confounding effects that inversely affects accuracy.
To, address this challenge, we propose to train a classification model based on generic semantic and syntactic features instead of the keywords-based features.
